### 2022-02-04 manuscript/manuscript.Rmd
Begin discussion

>>>>

# Discussion {.unnumbered}

This study aimed to develop accelerometer-based mechanical loading predition equations for jumps of diverse types and heights, testing different accelerometer placements and using both the resultant and vertical vectors. The results have shown that jumping pGRF prediction models based on accelerometry data have a lower accuracy compared to models developed for other activies, such as walking and running. Despite that, these models are the correct choice for this kind of activity eliciting hight levels of impact, as applying a model developed for walking in a sample similar to the current study yielded far worse results in terms of prediction accuracy. Also, as expected, the pLR prediction models performed poorly compared to the pGRF equations.
